---
title: "all_autosomes"
author: "Andy Beck"
date: "2024-11-12"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

Here in this document we will generate results for the rephrasing of probands from 602 trios along all 22 autosomes. We'll also compare rates of errors in the autosomes to what we observe in phasing 2000 X chromsome synthetic diploids.

```{r}
library(tidyverse)
library(yaml)
library(gtsummary)

library(grid)
library(gridExtra)


config_obj <- yaml::read_yaml("_config.yaml")

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

theme_set(theme_linedraw())

df_subj <- read_csv("data/1kgp/subject_info.csv")
ped_df <- read_table("data/1kgp/1kGP.3202_samples.pedigree_info.txt")

child_ids <- ped_df %>% filter(fatherID != "0" & motherID != "0") %>% pull(sampleID)
unrel_ids <- scan("data/1kgp/unrelated_subjects.txt", what = character())

df_subj_rel <- df_subj %>%
  filter(SAMPLE_NAME %in% child_ids)
df_subj_rel$id <- 1:602

df_subj_unrel <- df_subj %>%
  filter(SAMPLE_NAME %in% unrel_ids)

df_chrom_size <- read_tsv("data/hg38.chrom.sizes", n_max = 24, col_names = c("chrom", "bases"))

pair_info_df <- read_delim("data/sample_pairs.csv", col_names = c("POP", "ID1", "ID2"))
pair_info_df <- left_join(pair_info_df, {df_subj %>% select(SAMPLE_NAME, POPULATION, SUPER)}, by = c("ID1"="SAMPLE_NAME")) %>%
  select(-POPULATION)
pair_info_df$id <- 1:1000
```

## Data Reading

```{r}
# Load the heterozygous positions for a single individual
load_het_pos <- function(id, het_loc){
  f_name <- paste0(het_loc, "errors_", id, ".csv")
  df <- read_csv(f_name, show_col_types = F)
  df
}

# get error rates for individual subject
single_summary <- function(id, het_loc){
  df <- load_het_pos(id, het_loc)
  
  df %>%
    summarize(n_het = n(),
              n_het_cpg = sum(cpg),
              switch_b = sum(beagle_switch),
              switch_e = sum(eagle_switch),
              switch_s = sum(shapeit_switch),
              flip_b = sum(beagle_flip),
              flip_e = sum(eagle_flip),
              flip_s = sum(shapeit_flip),
              cpg_switch_b = sum(beagle_switch * cpg),
              cpg_switch_e = sum(eagle_switch * cpg),
              cpg_switch_s = sum(shapeit_switch * cpg),
              cpg_flip_b = sum(beagle_flip * cpg),
              cpg_flip_e = sum(eagle_flip * cpg),
              cpg_flip_s = sum(shapeit_flip * cpg)) %>%
    mutate(r_switch_b = switch_b / n_het,
           r_switch_e = switch_e / n_het,
           r_switch_s = switch_s / n_het,
           r_flip_b = flip_b / n_het,
           r_flip_e = flip_e / n_het,
           r_flip_s = flip_s / n_het,
           r_cpg_switch_b = cpg_switch_b / n_het_cpg,
           r_cpg_switch_e = cpg_switch_e / n_het_cpg,
           r_cpg_switch_s = cpg_switch_s / n_het_cpg,
           r_cpg_flip_b = cpg_flip_b / n_het_cpg,
           r_cpg_flip_e = cpg_flip_e / n_het_cpg,
           r_cpg_flip_s = cpg_flip_s / n_het_cpg
           )
}

all_summary <- function(ids, het_loc){
  results <- vector(mode = "list", length = length(ids))
  for(i in 1:length(ids)){
    results[[i]] <- single_summary(ids[i], het_loc)
    results[[i]]$id <- ids[i]
  }
  return(bind_rows(results))
}

load_premade_summary <- function(res_dir){
  f_name <- paste0(res_dir, "switch_errors/summary.csv")
  read_csv(f_name, show_col_types = F)
}
```

## Summary of all autosomes

```{r}
# df_1 <- all_summary(1:602, "output/trio_phase_1/het_loc/annotated/")
# df_1 <- df_1 %>%
#   left_join({df_subj_rel %>% select(SUPER, sex, id2) %>% rename(id=id2, pop = SUPER)})

df_1 <- load_premade_summary("output/trio_phase_1/")
df_2 <- load_premade_summary("output/trio_phase_2/")
df_3 <- load_premade_summary("output/trio_phase_3/")
df_4 <- load_premade_summary("output/trio_phase_4/")
df_5 <- load_premade_summary("output/trio_phase_5/")
df_6 <- load_premade_summary("output/trio_phase_6/")
df_7 <- load_premade_summary("output/trio_phase_7/")
df_8 <- load_premade_summary("output/trio_phase_8/")
df_9 <- load_premade_summary("output/trio_phase_9/")
df_10 <- load_premade_summary("output/trio_phase_10/")
df_11 <- load_premade_summary("output/trio_phase_11/")
df_12 <- load_premade_summary("output/trio_phase_12/")
df_13 <- load_premade_summary("output/trio_phase_13/")
df_14 <- load_premade_summary("output/trio_phase_14/")
df_15 <- load_premade_summary("output/trio_phase_15/")
df_16 <- load_premade_summary("output/trio_phase_16/")
df_17 <- load_premade_summary("output/trio_phase_17/")
df_18 <- load_premade_summary("output/trio_phase_18/")
df_19 <- load_premade_summary("output/trio_phase_19/")
df_20 <- load_premade_summary("output/trio_phase_20/")
df_21 <- load_premade_summary("output/trio_phase_21/")
df_22 <- load_premade_summary("output/trio_phase_22/")

df_1$chrom <- "1"
df_2$chrom <- "2"
df_3$chrom <- "3"
df_4$chrom <- "4"
df_5$chrom <- "5"
df_6$chrom <- "6"
df_7$chrom <- "7"
df_8$chrom <- "8"
df_9$chrom <- "9"
df_10$chrom <- "10"
df_11$chrom <- "11"
df_12$chrom <- "12"
df_13$chrom <- "13"
df_14$chrom <- "14"
df_15$chrom <- "15"
df_16$chrom <- "16"
df_17$chrom <- "17"
df_18$chrom <- "18"
df_19$chrom <- "19"
df_20$chrom <- "20"
df_21$chrom <- '21'
df_22$chrom <- "22"

df_x <- load_premade_summary("output/switch_errors/") %>% rename(SUPER = pop)
df_x$chrom <- "X"

df_all <- bind_rows(df_1, df_2, df_3, df_4, df_5, df_6, df_7, df_8, df_9, df_10,
                    df_11, df_12, df_13, df_14, df_15, df_16, df_17, df_18, df_19, df_20,
                    df_21, df_22, df_x)

df_all$chrom <- factor(df_all$chrom, levels = c(as.character(1:22), "X"))

df_all <-df_all %>%  
  mutate(Beagle_switch = n_other_beagle / n_hets,
         Eagle_switch = n_other_eagle / n_hets,
         SHAPEIT_switch = n_other_shapeit / n_hets,
         Beagle_flip = n_flip_beagle / n_hets,
         Eagle_flip = n_flip_eagle / n_hets,
         SHAPEIT_flip = n_flip_shapeit / n_hets)
```


Is it true that in general we observe a higher flip rate than switch rate in chromosome 1?

```{r}
switch_v_flip <- function(c_name){
  p1 <- df_all %>%
    filter(chrom == c_name) %>%
    mutate(r_switch_b = n_other_beagle / n_hets,
           r_flip_b = n_flip_beagle / n_hets) %>%
    ggplot(aes(x = r_switch_b, y = r_flip_b, color = SUPER)) +
    geom_point() +
    scale_colour_manual(values = cbPalette) +
    theme_classic() +
    geom_abline(slope = 1, intercept = 0) +
    xlab("Switch Rate") +
    ylab("Flip Rate") +
    ggtitle("Beagle")
  
  p_legend <- cowplot::get_legend(p1)
    
  p1 <- p1 + guides(colour="none")
  
  p2 <- df_all %>%
    filter(chrom == c_name) %>%
    mutate(r_switch_e = n_other_eagle / n_hets,
           r_flip_e = n_flip_eagle / n_hets) %>%
    ggplot(aes(x = r_switch_e, y = r_flip_e, color = SUPER)) +
    geom_point() +
    scale_colour_manual(values = cbPalette) +
    theme_classic() +
    geom_abline(slope = 1, intercept = 0) + guides(colour="none") +
    xlab("Switch Rate") +
    ylab("Flip Rate") +
    ggtitle("Eagle")
  
  p3 <- df_all %>%
    filter(chrom == c_name) %>%
    mutate(r_switch_s = n_other_shapeit / n_hets,
           r_flip_s = n_flip_shapeit / n_hets) %>%
    ggplot(aes(x = r_switch_s, y = r_flip_s, color = SUPER)) +
    geom_point() +
    scale_colour_manual(values = cbPalette) +
    theme_classic() +
    geom_abline(slope = 1, intercept = 0) + guides(colour="none") +
    xlab("Switch Rate") +
    ylab("Flip Rate") +
    ggtitle("SHAPEIT")
  
  final <- arrangeGrob(p1, p2, p3, p_legend, layout_matrix = rbind(c(1,2), c(3, 4)))
  return(final)
}

ggplotify::as.ggplot(switch_v_flip("1"))
ggplotify::as.ggplot(switch_v_flip("X"))
```

```{r message=FALSE, warning=FALSE}
for(c_name in c(as.character(1:22), "X")){
  print(c_name)
  print(ggplotify::as.ggplot(switch_v_flip(c_name)))
}
```

So we see a largely consistent pattern in the comparison of flip rates to switch rates along the autosomes. What's going on here? First, let's grab numeric summaries of this phenomenon:

```{r}
df_all  %>%
  mutate(Beagle = Beagle_flip / Beagle_switch,
         Eagle = Eagle_flip / Eagle_switch,
         SHAPEIT = SHAPEIT_flip / SHAPEIT_switch) %>%
  group_by(chrom) %>%
  summarize(Beagle = mean(Beagle),
            Eagle = mean(Eagle),
            SHAPEIT = mean(SHAPEIT)) %>%
  knitr::kable()
```

We see that for all the autosomes, the average ratio of the flip rate over the switch rate is greater than one for all three methods (this is also the case in chromosome X for SHAPEIT). Let's get a look at this by population:

```{r}
df_all %>%
  mutate(Beagle = Beagle_flip / Beagle_switch,
         Eagle = Eagle_flip / Eagle_switch,
         SHAPEIT = SHAPEIT_flip / SHAPEIT_switch) %>%
  group_by(chrom, SUPER) %>%
  summarize(Beagle = mean(Beagle),
            Eagle = mean(Eagle),
            SHAPEIT = mean(SHAPEIT)) %>%
  knitr::kable()

df_all %>%
  mutate(Beagle = Beagle_flip / Beagle_switch,
         Eagle = Eagle_flip / Eagle_switch,
         SHAPEIT = SHAPEIT_flip / SHAPEIT_switch) %>%
  group_by(chrom, SUPER) %>%
  summarize(Beagle = mean(Beagle),
            Eagle = mean(Eagle),
            SHAPEIT = mean(SHAPEIT)) %>%
  pivot_longer(Beagle:SHAPEIT, names_to = "method", values_to = "flip_switch_ratio") %>%
  ggplot(aes(x = chrom, y = flip_switch_ratio, color = method)) +
  geom_point() +
  facet_grid(rows = vars(SUPER)) +
  ylab("Flip Rate / Switch Rate") +
  xlab("Chromosome") +
  scale_colour_manual(values = cbPalette) +
  labs(color = "Method") +
  theme_linedraw()
```

## Chromosome Comparisons

### Mean number of heterozygous sites

```{r}
df_all %>%
  group_by(chrom, SUPER) %>%
  summarize(hets = mean(n_hets),
            hets_cpg = mean(n_het_cpg)) %>%
  ggplot(aes(x = chrom, y = hets, colour = SUPER)) +
  geom_point() +
  scale_colour_manual(values = cbPalette) +
  xlab("Chromosome") +
  ylab("Mean Size (# Het.)") +
  labs(color = "Population")
```

### Recombination rates

```{r}
read_rr <- function(chrom){
  df_rr <- read_tsv(paste0("data/decode/chr", chrom, "_recomb.bed"),
                    show_col_types = F,
                    col_names = c("chrom", "begin", "end", "rr"))
  df_rr
}
plot_rr_window <- function(chrom, bin_size = 1e6){
  df_rr <- read_rr(chrom)
  df_rr <- df_rr %>%
    mutate(bin = ceiling(begin / bin_size)) %>%
    group_by(bin) %>%
    summarize(rr= mean(rr))
  
  p <- df_rr %>%
    ggplot(aes(x = bin, y = rr)) +
    geom_point() +
    xlab("Bin") +
    ylab("Recombination Rate")
  
  return(p)
}
```

#### MB Scale

```{r}
for(i in c(1:22, "X")){
  print(plot_rr_window(i) + ggtitle(paste0("Chromosome ", i)))
}
```

#### 100KB

```{r}
for(i in c(1:22, "X")){
  print(plot_rr_window(i, bin_size = 1e5) + ggtitle(paste0("Chromosome ", i)))
}
```

#### No bins

```{r}
for(i in c(1:22, "X")){
  print(plot_rr_window(i, bin_size = 1) + ggtitle(paste0("Chromosome ", i)))
}
```


## Switch Error Rates

Considering only switch errors, what do the rates we observe in the autosomes look like compared to what we observe in X?

```{r}
df_all %>%
  group_by(SUPER, chrom) %>%
  summarize(Beagle = mean(Beagle_switch),
            Eagle = mean(Eagle_switch),
            SHAPEIT = mean(SHAPEIT_switch)) %>%
  pivot_longer(Beagle:SHAPEIT, names_to = "Method", values_to = "switch") %>%
  ggplot(aes(x = chrom, y = switch, color = Method)) +
  geom_point() +
  theme_linedraw() +
  scale_colour_manual(values = cbPalette) +
  ylab("Mean Switch Rate") +
  facet_grid(rows = vars(SUPER)) +
  xlab("Chromosome")
```

```{r}
df_all %>%
  group_by(chrom, SUPER) %>%
  summarize(Beagle = mean(Beagle_switch),
            Eagle = mean(Eagle_switch),
            SHAPEIT = mean(SHAPEIT_switch)) %>%
  knitr::kable()
```

## Flip Error Rates

What do the flip error rates look like in the autosomes (compared to X)?

```{r}
df_all %>%
  group_by(SUPER, chrom) %>%
  summarize(Beagle = mean(Beagle_flip),
            Eagle = mean(Eagle_flip),
            SHAPEIT = mean(SHAPEIT_flip)) %>%
  pivot_longer(Beagle:SHAPEIT, names_to = "Method", values_to = "flip") %>%
  ggplot(aes(x = chrom, y = flip, color = Method)) +
  geom_point() +
  scale_colour_manual(values = cbPalette) +
  ylab("Mean Flip Rate") +
  facet_grid(rows = vars(SUPER)) +
  xlab("Chromosome")
```

```{r}
df_all %>%
  group_by(chrom, SUPER) %>%
  summarize(Beagle = mean(Beagle_flip),
            Eagle = mean(Eagle_flip),
            SHAPEIT = mean(SHAPEIT_flip)) %>%
  knitr::kable()
```

## Error distributions across bins

### Data Loading Functions

```{r}
single_bin_counts <- function(id, het_loc, bin_size = 1e6){
  df_het <- load_het_pos(id, het_loc)
  
  df_het$bin <- ceiling(df_het$pos / bin_size)
  
  final <- df_het %>%
    group_by(bin) %>%
    summarize(s_b = sum(beagle_switch),
              s_e = sum(eagle_switch),
              s_s = sum(shapeit_switch),
              f_b = sum(beagle_flip),
              f_e = sum(eagle_flip),
              f_s = sum(shapeit_flip),
              n_het = n(),
              n_het_cpg = sum(cpg),
              cpg_s_b = sum(cpg * beagle_switch),
              cpg_s_e = sum(cpg * eagle_switch),
              cpg_s_s = sum(cpg * shapeit_switch),
              cpg_f_b = sum(cpg * beagle_flip),
              cpg_f_e = sum(cpg * eagle_flip),
              cpg_f_s = sum(cpg * shapeit_flip))
  
  final$id <- id
  return(final)
}

all_counts <- function(ids, het_loc, df_subj_rel, bin_size = 1e6){
  final <- vector(mode = "list", length = length(ids))
  for(i in 1:length(ids)){
    final[[i]] <- single_bin_counts(ids[i], het_loc)
  }
  return(bind_rows(final) %>% left_join({df_subj_rel %>% select(id, SUPER)}, by = "id"))
}

```

### Plotting Functions

```{r}
plot_switch_rate_bin <- function(df, chrom, bin_label="MB"){
  p <- df %>%
    filter(chrom == chrom) %>%
    mutate(Beagle = s_b / n_het,
           Eagle = s_e / n_het,
           SHAPEIT = s_s / n_het) %>%
    group_by(SUPER, bin) %>%
    summarize(Beagle = mean(Beagle),
              Eagle = mean(Eagle),
              SHAPEIT = mean(SHAPEIT)) %>%
    pivot_longer(Beagle:SHAPEIT, values_to = "switch_rate", names_to = "Method") %>%
    ggplot(aes(x = bin, y = switch_rate, colour = Method)) +
    geom_point() +
    xlab(paste0("Bin (", bin_label, ")")) +
    ylab("Switch Rate") +
    ggtitle(paste0("Chromosome ", chrom)) +
    facet_grid(rows = vars(SUPER))
  return(p)
}

plot_flip_rate_bin <- function(df, chrom, bin_label="MB"){
  p <- df %>%
    filter(chrom == chrom) %>%
    mutate(Beagle = f_b / n_het,
           Eagle = f_e / n_het,
           SHAPEIT = f_s / n_het) %>%
    group_by(SUPER, bin) %>%
    summarize(Beagle = mean(Beagle),
              Eagle = mean(Eagle),
              SHAPEIT = mean(SHAPEIT)) %>%
    pivot_longer(Beagle:SHAPEIT, values_to = "flip_rate", names_to = "Method") %>%
    ggplot(aes(x = bin, y = flip_rate, colour = Method)) +
    geom_point() +
    xlab(paste0("Bin (", bin_label, ")")) +
    ylab("Flip Rate") +
    ggtitle(paste0("Chromosome ", chrom)) +
    facet_grid(rows = vars(SUPER))
  return(p)
}

plot_error_rate_bin <- function(df, chrom, bin_label="MB"){
  p <- df %>%
    filter(chrom == chrom) %>%
    mutate(Beagle = (s_b + f_b) / n_het,
           Eagle = (s_e + f_e) / n_het,
           SHAPEIT = (s_s + f_s) / n_het) %>%
    group_by(SUPER, bin) %>%
    summarize(Beagle = mean(Beagle),
              Eagle = mean(Eagle),
              SHAPEIT = mean(SHAPEIT)) %>%
    pivot_longer(Beagle:SHAPEIT, values_to = "error_rate", names_to = "Method") %>%
    ggplot(aes(x = bin, y = error_rate, colour = Method)) +
    geom_point() +
    xlab(paste0("Bin (", bin_label, ")")) +
    ylab("Error Rate") +
    ggtitle(paste0("Chromosome ", chrom)) +
    facet_grid(rows = vars(SUPER))
  return(p)
}

plot_switches_bin <- function(df, chrom, bin_label="MB"){
  p <- df %>%
    filter(chrom == chrom) %>%
    mutate(Beagle = s_b,
           Eagle = s_e,
           SHAPEIT = s_s) %>%
    group_by(SUPER, bin) %>%
    summarize(Beagle = mean(Beagle),
              Eagle = mean(Eagle),
              SHAPEIT = mean(SHAPEIT)) %>%
    pivot_longer(Beagle:SHAPEIT, values_to = "switch_rate", names_to = "Method") %>%
    ggplot(aes(x = bin, y = switch_rate, colour = Method)) +
    geom_point() +
    xlab(paste0("Bin (", bin_label, ")")) +
    ylab("Switchs") +
    ggtitle(paste0("Chromosome ", chrom)) +
    facet_grid(rows = vars(SUPER))
  return(p)
}

plot_flips_bin <- function(df, chrom, bin_label="MB"){
  p <- df %>%
    filter(chrom == chrom) %>%
    mutate(Beagle = f_b,
           Eagle = f_e,
           SHAPEIT = f_s) %>%
    group_by(SUPER, bin) %>%
    summarize(Beagle = mean(Beagle),
              Eagle = mean(Eagle),
              SHAPEIT = mean(SHAPEIT)) %>%
    pivot_longer(Beagle:SHAPEIT, values_to = "flip_rate", names_to = "Method") %>%
    ggplot(aes(x = bin, y = flip_rate, colour = Method)) +
    geom_point() +
    xlab(paste0("Bin (", bin_label, ")")) +
    ylab("Flips") +
    ggtitle(paste0("Chromosome ", chrom)) +
    facet_grid(rows = vars(SUPER))
  return(p)
}

plot_errors_bin <- function(df, chrom, bin_label="MB"){
  p <- df %>%
    filter(chrom == chrom) %>%
    mutate(Beagle = (s_b + f_b),
           Eagle = (s_e + f_e),
           SHAPEIT = (s_s + f_s)) %>%
    group_by(SUPER, bin) %>%
    summarize(Beagle = mean(Beagle),
              Eagle = mean(Eagle),
              SHAPEIT = mean(SHAPEIT)) %>%
    pivot_longer(Beagle:SHAPEIT, values_to = "error_rate", names_to = "Method") %>%
    ggplot(aes(x = bin, y = error_rate, colour = Method)) +
    geom_point() +
    xlab(paste0("Bin (", bin_label, ")")) +
    ylab("Errors") +
    ggtitle(paste0("Chromosome ", chrom)) +
    facet_grid(rows = vars(SUPER))
  return(p)
}
```

### Load the data for all chromosomes

```{r}
# library(parallel)
# library(foreach)
# library(doParallel)
# registerDoParallel(22)
# list_MB <- foreach (i=1:22) %dopar% {
#   all_counts(1:602, paste0("output/trio_phase_", i, "/het_loc/annotated/"), df_subj_rel = df_subj_rel, bin_size = 1e6)
# }
# stopImplicitCluster()
# 
# for(i in 1:22){
#   list_MB[[i]]$chrom <- as.character(i)
# }
# 
# all_MB <- bind_rows(list_MB)
# 
# df_X_MB <- all_counts(1:1000, "output/switch_errors/het_loc/annotated/", pair_info_df, bin_size = 1e6 )
# df_X_MB$chrom <- "X"
# 
# all_MB <- all_MB %>% bind_rows(df_X_MB)
# 
# write_csv(all_MB, "output/error_rate_MB.csv")

df_all_MB <- read_csv("output/error_rate_MB.csv")
```

```{r}
plot_switch_rate_bin(df_all_MB, "X") + scale_colour_manual(values = cbPalette)
plot_flip_rate_bin(df_all_MB, "X") + scale_colour_manual(values = cbPalette)

df_all_MB %>%
  filter(chrom == "X") %>%
  group_by(bin, SUPER) %>%
  summarize(flip = mean(f_b / n_het),
            switch = mean(s_b / n_het)) %>%
  ggplot(aes(flip, switch)) +
  geom_point() +
  geom_abline(slope = 1, intercept = 0) +
  facet_grid(cols = vars(SUPER)) +
  xlab("Flip Rate") +
  ylab("Switch Rate") +
  ggtitle(paste0("Chromosome ", "X"))
```


```{r, fig.width=9.75, fig.height=2.5}
for(chromo in c(as.character(1:22), "X")){
  p <- df_all_MB %>%
    filter(chrom == chromo) %>%
    group_by(bin, SUPER) %>%
    summarize(flip = mean(f_b / n_het),
              switch = mean(s_b / n_het)) %>%
    ggplot(aes(flip, switch)) +
    geom_point() +
    geom_abline(slope = 1, intercept = 0) +
    facet_grid(cols = vars(SUPER)) +
    xlab("Flip Rate") +
    ylab("Switch Rate") +
    ggtitle(paste0("Chromosome ", chromo, "; Beagle"))
  print(p)
}

for(chromo in c(as.character(1:22), "X")){
  p <- df_all_MB %>%
    filter(chrom == chromo) %>%
    group_by(bin, SUPER) %>%
    summarize(flip = mean(f_e / n_het),
              switch = mean(s_e / n_het)) %>%
    ggplot(aes(flip, switch)) +
    geom_point() +
    geom_abline(slope = 1, intercept = 0) +
    facet_grid(cols = vars(SUPER)) +
    xlab("Flip Rate") +
    ylab("Switch Rate") +
    ggtitle(paste0("Chromosome ", chromo, "; Eagle"))
  print(p)
}

for(chromo in c(as.character(1:22), "X")){
  p <- df_all_MB %>%
    filter(chrom == chromo) %>%
    group_by(bin, SUPER) %>%
    summarize(flip = mean(f_s / n_het),
              switch = mean(s_s / n_het)) %>%
    ggplot(aes(flip, switch)) +
    geom_point() +
    geom_abline(slope = 1, intercept = 0) +
    facet_grid(cols = vars(SUPER)) +
    xlab("Flip Rate") +
    ylab("Switch Rate") +
    ggtitle(paste0("Chromosome ", chromo, "; SHAPEIT"))
  print(p)
}
```

## Errors and RR in bins

### Switches

```{r, fig.width=10, fig.height=3}

for(i in c(as.character(1:22), "X")){
  df_X_rr <- read_rr(i) %>%
    mutate(bin = ceiling(begin / 1e6)) %>%
    group_by(bin) %>%
    summarize(rr = mean(rr))
  
  df_X_rr <- df_X_rr %>%
    right_join({df_all_MB %>% filter(chrom == i)}, by="bin")
  
  p <- df_X_rr %>%
    mutate(Beagle = s_b ,
           Eagle = s_e ,
           SHAPEIT = s_s ) %>%
    group_by(bin, SUPER) %>%
    summarise(rr = mean(rr),
              Beagle = mean(Beagle),
              Eagle = mean(Eagle),
              SHAPEIT = mean(SHAPEIT)) %>%
    pivot_longer(Beagle:SHAPEIT, names_to = "Method", values_to = "switch_rate") %>%
    drop_na() %>%
    ggplot(aes(x = rr, y = switch_rate, color = Method)) +
    geom_point() +
    xlab("Recombination Rate") +
    ylab("Switches") +
    ggtitle("Switchs and Recombination Rates (MB)", paste0("Chromosome ", i)) +
    facet_grid(cols=vars(SUPER))
  print(p)
  
  df_X_rr %>%
    mutate(Beagle = s_b ,
           Eagle = s_e ,
           SHAPEIT = s_s ) %>%
    group_by(bin, SUPER) %>%
    summarise(rr = mean(rr),
              Beagle = mean(Beagle),
              Eagle = mean(Eagle),
              SHAPEIT = mean(SHAPEIT)) %>%
    select(-bin) %>%
    corrr::correlate()
}
```

### Flips

```{r, fig.width=10, fig.height=3}

for(i in c(as.character(1:22), "X")){
  df_X_rr <- read_rr(i) %>%
    mutate(bin = ceiling(begin / 1e6)) %>%
    group_by(bin) %>%
    summarize(rr = mean(rr))
  
  df_X_rr <- df_X_rr %>%
    right_join({df_all_MB %>% filter(chrom == i)}, by="bin")
  
  p <- df_X_rr %>%
    mutate(Beagle = f_b ,
           Eagle = f_e ,
           SHAPEIT = f_s ) %>%
    group_by(bin, SUPER) %>%
    summarise(rr = mean(rr),
              Beagle = mean(Beagle),
              Eagle = mean(Eagle),
              SHAPEIT = mean(SHAPEIT)) %>%
    pivot_longer(Beagle:SHAPEIT, names_to = "Method", values_to = "switch_rate") %>%
    drop_na() %>%
    ggplot(aes(x = rr, y = switch_rate, color = Method)) +
    geom_point() +
    xlab("Recombination Rate") +
    ylab("Flips") +
    ggtitle("Flips and Recombination Rates (MB)", paste0("Chromosome ", i)) +
    facet_grid(cols=vars(SUPER))
  print(p)
  
  df_X_rr %>%
    mutate(Beagle = f_b ,
           Eagle = f_e ,
           SHAPEIT = f_s ) %>%
    group_by(bin, SUPER) %>%
    summarise(rr = mean(rr),
              Beagle = mean(Beagle),
              Eagle = mean(Eagle),
              SHAPEIT = mean(SHAPEIT)) %>%
    ungroup() %>%
    select(-bin) %>%
    corrr::correlate()
}
```

## CpG Enrichment

### Switches

```{r}
df_all %>%
    filter(chrom == "1") %>%
    mutate(Beagle = (n_other_cpg_beagle / n_het_cpg)/(n_other_beagle / n_hets),
           Eagle = (n_other_cpg_eagle / n_het_cpg)/(n_other_eagle / n_hets),
           SHAPEIT = (n_other_cpg_shapeit / n_het_cpg)/(n_other_shapeit / n_hets)) %>%
    select(Beagle:SHAPEIT, SUPER) %>%
    pivot_longer(-SUPER, names_to = "Method", values_to = "enrich") %>%
    ggplot(aes(x = Method, y = enrich)) +
    geom_boxplot() +
    ggtitle("Enrichment of Switches at CpG", paste0("Chromosome ", "X")) +
    ylab("Enrichment") +
    geom_hline(yintercept = 1, colour = "red")

df_all %>%
    filter(chrom == "X") %>%
    mutate(Beagle = (n_flip_cpg_beagle / n_het_cpg)/(n_flip_beagle / n_hets),
           Eagle = (n_flip_cpg_eagle / n_het_cpg)/(n_flip_eagle / n_hets),
           SHAPEIT = (n_flip_cpg_shapeit / n_het_cpg)/(n_flip_shapeit / n_hets)) %>%
    select(Beagle:SHAPEIT, SUPER) %>%
    pivot_longer(-SUPER, names_to = "Method", values_to = "enrich") %>%
    ggplot(aes(x = Method, y = enrich)) +
    geom_boxplot() +
    ggtitle("Enrichment of Flips at CpG", paste0("Chromosome ", "X")) +
    ylab("Enrichment") +
    geom_hline(yintercept = 1, colour = "red") +
  facet_grid(cols = vars(SUPER)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```


```{r, fig.height=4, fig.width=5}
for(i in c(as.character(1:22), "X") ){
  p <- df_all %>%
    filter(chrom == i) %>%
    mutate(Beagle = (n_other_cpg_beagle / n_het_cpg)/(n_other_beagle / n_hets),
           Eagle = (n_other_cpg_eagle / n_het_cpg)/(n_other_eagle / n_hets),
           SHAPEIT = (n_other_cpg_shapeit / n_het_cpg)/(n_other_shapeit / n_hets)) %>%
    select(Beagle:SHAPEIT, SUPER) %>%
    pivot_longer(-SUPER, names_to = "Method", values_to = "enrich") %>%
    ggplot(aes(x = Method, y = enrich)) +
    geom_boxplot() +
    ggtitle("Enrichment of Switches at CpG", paste0("Chromosome ", i)) +
    ylab("Enrichment") +
    geom_hline(yintercept = 1, colour = "red")
  print(p)
}

for(i in c(as.character(1:22), "X") ){
  p <- df_all %>%
    filter(chrom == i) %>%
    mutate(Beagle = (n_flip_cpg_beagle / n_het_cpg)/(n_flip_beagle / n_hets),
           Eagle = (n_flip_cpg_eagle / n_het_cpg)/(n_flip_eagle / n_hets),
           SHAPEIT = (n_flip_cpg_shapeit / n_het_cpg)/(n_flip_shapeit / n_hets)) %>%
    select(Beagle:SHAPEIT, SUPER) %>%
    pivot_longer(-SUPER, names_to = "Method", values_to = "enrich") %>%
    ggplot(aes(x = Method, y = enrich)) +
    geom_boxplot() +
    ggtitle("Enrichment of Flips at CpG", paste0("Chromosome ", i)) +
    ylab("Enrichment") +
    geom_hline(yintercept = 1, colour = "red")
  print(p)
}
```

```{r, fig.height=4, fig.width=8}
for(i in c(as.character(1:22), "X") ){
  p <- df_all %>%
    filter(chrom == i) %>%
    mutate(Beagle = (n_other_cpg_beagle / n_het_cpg)/(n_other_beagle / n_hets),
           Eagle = (n_other_cpg_eagle / n_het_cpg)/(n_other_eagle / n_hets),
           SHAPEIT = (n_other_cpg_shapeit / n_het_cpg)/(n_other_shapeit / n_hets)) %>%
    select(Beagle:SHAPEIT, SUPER) %>%
    pivot_longer(-SUPER, names_to = "Method", values_to = "enrich") %>%
    ggplot(aes(x = Method, y = enrich)) +
    geom_boxplot() +
    ggtitle("Enrichment of Switches at CpG", paste0("Chromosome ", i)) +
    ylab("Enrichment") +
    geom_hline(yintercept = 1, colour = "red") +
    facet_grid(cols = vars(SUPER)) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
  print(p)
}

for(i in c(as.character(1:22), "X") ){
  p <- df_all %>%
    filter(chrom == i) %>%
    mutate(Beagle = (n_flip_cpg_beagle / n_het_cpg)/(n_flip_beagle / n_hets),
           Eagle = (n_flip_cpg_eagle / n_het_cpg)/(n_flip_eagle / n_hets),
           SHAPEIT = (n_flip_cpg_shapeit / n_het_cpg)/(n_flip_shapeit / n_hets)) %>%
    select(Beagle:SHAPEIT, SUPER) %>%
    pivot_longer(-SUPER, names_to = "Method", values_to = "enrich") %>%
    ggplot(aes(x = Method, y = enrich)) +
    geom_boxplot() +
    ggtitle("Enrichment of Flips at CpG", paste0("Chromosome ", i)) +
    ylab("Enrichment") +
    geom_hline(yintercept = 1, colour = "red") +
    facet_grid(cols = vars(SUPER)) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
  print(p)
}
```

