---
title: "Voting Method Results"
author: "Andy Beck"
date: "2024-06-27"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r, message=FALSE, warning=FALSE, results = 'hide'}
library(tidyverse)
library(grid)
library(gridExtra) 
library(yaml)

config_obj <- yaml::read_yaml("_config.yaml")
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000")
```


## Subject Information

### Chromosome X Synthetic Diploids

```{r}
sample_info_df <- read_csv("data/1kgp/subject_info.csv") %>%
  select(SAMPLE_NAME, POPULATION, SUPER)

pair_info_df <- read_delim("data/sample_pairs.csv", col_names = c("POP", "ID1", "ID2"))
pair_info_df <- left_join(pair_info_df, sample_info_df, by = c("ID1"="SAMPLE_NAME")) %>%
  rename(SP = SUPER) %>%
  select(-POPULATION)

pair_info_df$pair_id <- 1:1000
```

### Trio Probands

```{r}
ped_df <- read_table("data/1kgp/1kGP.3202_samples.pedigree_info.txt")

child_ids <- ped_df %>% filter(fatherID != "0" & motherID != "0") %>% pull(sampleID)
unrel_ids <- scan("data/1kgp/unrelated_subjects.txt", what = character())

df_subj_rel <- sample_info_df %>%
  filter(SAMPLE_NAME %in% child_ids)
df_subj_rel$id2 <- 1:602

df_subj_unrel <- sample_info_df %>%
  filter(SAMPLE_NAME %in% unrel_ids)
```


## Chromosome X Results

```{r}
df_switch_x <- read_csv(paste0(config_obj$base_dir, "/output/switch_errors/switch_errors/summary.csv"), show_col_types = F)

df_vote_x <- read_csv(paste0(config_obj$base_dir, "/output/vote_x/summary.csv"), show_col_types = F)
```

Let's first look at the number of switches and flips per synthetic diploid across methods:

```{r}
df_x <- df_switch_x %>%
  select(((contains("n_other") | contains("n_flip")) & !contains("cpg")), pair_id) %>%
  pivot_longer(-pair_id, names_to = c("drop","error", "method"), names_sep = "_", values_to = "n") %>%
  select(-drop) %>%
  pivot_wider(names_from = "error", values_from = "n", id_cols = c("pair_id","method")) %>%
  rename(switches = other) %>%
  bind_rows({
    df_vote_x %>%
      select(((contains("n_other") | contains("n_flip")) & !contains("cpg")), pair_id) %>%
      pivot_longer(-pair_id, names_to = c("drop","error", "method"), names_sep = "_", values_to = "n") %>%
      select(-drop) %>%
      pivot_wider(names_from = "error", values_from = "n", id_cols = c("pair_id","method")) %>%
      rename(switches = other)
  }) %>%
  arrange(pair_id)

df_x <- df_x %>%
  left_join({pair_info_df %>% select(pair_id, SP)})

df_x %>%
  pivot_longer(switches:flip, names_to = "error_type", values_to = "n") %>%
  mutate(method = factor(method, levels = c("beagle", "eagle", "shapeit", "vote"), labels = c("Beagle", "Eagle", "SHAPEIT", "Vote"))) %>%
  ggplot(aes(x = error_type, y = n, color = method)) +
  geom_boxplot() +
  xlab("Error Type") +
  ylab("Errors") +
  scale_color_manual(values = cbPalette) +
  labs(color = "Method")
```

Let's see if there are population-level differences:

```{r}
df_x %>%
  ggplot(aes(x = method, y = switches, colour = SP)) +
  geom_boxplot() +
  xlab("Method") +
  ylab("Switches") +
  labs(colour = "Population") +
  scale_colour_manual(values = cbPalette)

df_x %>%
  ggplot(aes(x = method, y = flip, colour = SP)) +
  geom_boxplot() +
  xlab("Method") +
  ylab("Flips") +
  labs(colour = "Population") +
  scale_colour_manual(values = cbPalette)
```

And finally, let's look at each pair of methods and each individual synthetic diploid:

```{r}
sub_plot <- function(df, x, y, x_lab, y_lab){
  p1 <- df %>%
    ggplot(aes(x = !! sym(x), y = !! sym(y), colour = SP)) +
    geom_point() +
    geom_abline(slope = 1, intercept = 0, linetype = "dotdash") +
    xlab(x_lab) +
    ylab(y_lab) +
    scale_color_manual(values = cbPalette) +
    labs(colour = "Population") +
    theme_classic()
  return(p1)
}

pairwise_plots <- function(df, type = "switches"){
  df_plot <- df %>%
    select(pair_id, SP, method, !! sym(type)) %>%
    pivot_wider(names_from = method, values_from = !! sym(type), id_cols = c("pair_id", "SP"))
  
  p1 <- sub_plot(df_plot, "vote", "beagle", "Vote", "Beagle")
  p_legend <- cowplot::get_legend(p1)
  p1 <- p1 + guides(colour="none")
  
  p2 <- sub_plot(df_plot, "shapeit", "beagle", "SHAPEIT", "Beagle") + guides(colour="none")
  p3 <- sub_plot(df_plot, "eagle", "beagle", "Eagle", "Beagle") + guides(colour="none")
  
  p4 <- sub_plot(df_plot, "vote", "eagle", "Vote", "Eagle") + guides(colour="none")
  p5 <- sub_plot(df_plot, "shapeit", "eagle", "SHAPEIT", "Eagle") + guides(colour="none")
  
  p6 <- sub_plot(df_plot, "vote", "shapeit", "Vote", "SHAPEIT") + guides(colour="none")
  
  return(grid.arrange(p1, p2, p3, p4, p5, p6, p_legend, 
               layout_matrix = rbind(c(1,2,3), c(4, 5, NA), c(6, NA, 7))))
}
```

```{r, fig.width=8, fig.height=8}
pairwise_plots(df_x, "switches")
```

```{r, fig.width=8, fig.height=7}
pairwise_plots(df_x, "flip")
```


## Chromosome 15

```{r}
df_switch_15 <- read_csv(paste0(config_obj$base_dir, "/output/trio_phase_15/switch_errors/summary.csv"), show_col_types = F)

df_vote_15 <- read_csv(paste0(config_obj$base_dir, "/output/vote_15/summary.csv"), show_col_types = F)

df_15 <- df_switch_15 %>%
  select(((contains("n_other") | contains("n_flip")) & !contains("cpg")), pair_id) %>%
  pivot_longer(-pair_id, names_to = c("drop","error", "method"), names_sep = "_", values_to = "n") %>%
  select(-drop) %>%
  pivot_wider(names_from = "error", values_from = "n", id_cols = c("pair_id","method")) %>%
  rename(switches = other) %>%
  bind_rows({
    df_vote_15 %>%
      select(((contains("n_other") | contains("n_flip")) & !contains("cpg")), pair_id) %>%
      pivot_longer(-pair_id, names_to = c("drop","error", "method"), names_sep = "_", values_to = "n") %>%
      select(-drop) %>%
      pivot_wider(names_from = "error", values_from = "n", id_cols = c("pair_id","method")) %>%
      rename(switches = other)
  }) %>%
  arrange(pair_id)

df_15 <- df_15 %>%
  left_join({df_subj_rel %>% select(id2, SUPER) %>% rename(pair_id = id2, SP = SUPER)})
```

```{r}
df_15 %>%
  pivot_longer(switches:flip, names_to = "error_type", values_to = "n") %>%
  mutate(method = factor(method, levels = c("beagle", "eagle", "shapeit", "vote"), labels = c("Beagle", "Eagle", "SHAPEIT", "Vote"))) %>%
  ggplot(aes(x = error_type, y = n, color = method)) +
  geom_boxplot() +
  xlab("Error Type") +
  ylab("Errors") +
  scale_color_manual(values = cbPalette) +
  labs(color = "Method")
```

Let's see if there are population-level differences:

```{r}
df_15 %>%
  ggplot(aes(x = method, y = switches, colour = SP)) +
  geom_boxplot() +
  xlab("Method") +
  ylab("Switches") +
  labs(colour = "Population") +
  scale_colour_manual(values = cbPalette)

df_15 %>%
  ggplot(aes(x = method, y = flip, colour = SP)) +
  geom_boxplot() +
  xlab("Method") +
  ylab("Flips") +
  labs(colour = "Population") +
  scale_colour_manual(values = cbPalette)
```

```{r, fig.width=8, fig.height=8}
pairwise_plots(df_15, "switches")
```

```{r, fig.width=8, fig.height=7}
pairwise_plots(df_15, "flip")
```
